\documentclass[12pt]{article}
\usepackage{a4} 
\usepackage{hyperref} 
\usepackage{color}
\usepackage{graphicx} 
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{bm}
\usepackage[lofdepth,lotdepth]{subfig}

\relpenalty=10000
\binoppenalty=10000

% Set page size:

\textwidth 160mm 
\textheight 235mm 
\oddsidemargin 0mm 
\topmargin -15mm
\baselineskip 13pt
\parskip 0pc 
\parindent 1pc

% Headers and footer using fancyhdr:

\definecolor{darkred}{rgb}{0.80,0.00,0.05}
\definecolor{blue}{rgb}{0.00,0.00,0.95}
\definecolor{darkgreen}{rgb}{0.00,0.60,0.0}
\definecolor{gray}{rgb}{0.95,0.9,0.9}

\title{Theoretical and Numerical Study of Models of Entanglement for
  Neutrons}

\date{14 May, 2012} 

\author{ Candidate Number: 8221T \\ Supervisor: Dr Crispin Barnes }

\begin{document} 

\maketitle

\input{abstract}

\input{introduction}

\input{experiment}

\input{model}

\input{results}

\input{conclusions}

\newpage

\input{appendix}

\input{decoherence}

\begin{thebibliography}{9}

\bibitem{pulsar} J.M. Weisberg, J. H. Taylor, \emph{Relativistic
  Binary Pulsar B1913+16: Thirty Years of Observations and Analysis},
  arXiv:astro-ph/0407149v1 (2004).

\bibitem{hobson} M. P. Hobson, G. Efstathiou, A. N. Lasenby,
  \emph{General Relativity: An Introduction for Physicists},
  (ch. 17-18), Cambridge University Press, 2009.  ISBN-13
  978-0-521-82951-9.

\bibitem{epr}
  A. Einstein, B. Podolsky, N. Rosen, 
  \emph{Can Quantum-Mechanical Description of Physical Reality Be Considered Complete?}
  Phys. Rev. 47, 777–780
  (1935).

\bibitem{aspect} A. Aspect, J. Dalibard, G. Roger, \emph{Experimental
  Test of Bell's Inequalities Using Time-Varying Analyzers}
  Phys. Rev. Lett. 49, 1804-1807 (1982).

\bibitem{steane} A. Steane, \emph{Quantum Computing},
  arXiv:quant-ph/9708022v2 (1997).

\bibitem{zurek} W. H. Zurek, \emph{Decoherence and the transition from
  quantum to classical -- REVISITED} arXiv:quant-ph/0306072v1 (2003).

\bibitem{edmund} E. T. Owen, M. C. Dean, C. H. W. Barnes,
  \emph{Generation of Entanglement between Qubits in a One-Dimensional
    Harmonic Oscillator}, Phys. Rev. A 85, 022319 (2012).

\bibitem{rings}
  http://www.johnstonsarchive.net/relativity/pictures.html

\bibitem{blundell} S. J. Blundell, J. A. C. Bland, \emph{Polarized
  Neutron Reflection as a Probe of Magnetic Films and Multilayers},
  Phys. Rev. B 46, 3391-3400 (1992).

\bibitem{kobzarev} I.Y. Kobzarev, L.B. Okun, \emph{Gravitational
  Interaction of Fermions}, Soviet Journal of Experimental and
  Theoretical Physics, Vol. 16, p.1343 (1963).

\bibitem{decoherence} T. Fujisawa, T. Hayashi, H. D. Cheong,
  Y. H. Jeong, Y. Hirayama, \emph{Rotation and Phase-shift Operations
    for a Charge Qubit in a Double Quantum Dot}, Phys. Rev. Lett 91
  226804-1 (2003).

\bibitem{numerics} J. J. V. Maestri, R. H. Landau, M. J. Paez,
  \emph{Two-Particle Schroedinger Equation Animations of
    Wavepacket-Wavepacket Scattering (revised)},
  arXiv:physics/9909042v1 [physics.comp-ph] (2008).

\bibitem{feynman} R. P. Feynman, F. L. Vernon Jr., \emph{The theory of
  a general quantum system interacting with a linear dissipative
  system}, Annals Phys. 24, 118-173 (1963).

\bibitem{caldeira} A. O. Caldeira, A. J. Leggett, \emph{Path Integral
  Approach to Quantum Brownian Motion}, Physica 121A, 587-616 (1983).

\bibitem{master} W. G. Unruh, W. H. Zurek, \emph{Reduction of a wave
  packet in quantum Brownian motion}, Phys. Rev. D. 40, 1071-1094
  (1984).

\end{thebibliography}

\end{document}
